### 2016-11-16 capability-machine.tex
Added heap satisfaction
Added an akward like example

%% make latex preview-mode work with natbib...
\usepackage[displaymath,floats,graphics,textmath,footnotes]{preview}
%\PreviewMacro*{\cofes{}} This brings compiling for non-auctex to a grinding halt.

@@

@@

Erase all but a set of views:
\begin{align*}
  \erase{W}{S} \defeq \lambda r \ldotp 
  \begin{cases}
    W(r) & W(r).v \in S\\
    \bot & \text{otherwise}
  \end{cases}
\end{align*}

@@

\begin{definition}[Heap satisfaction/erasure]
\begin{align*}
&\heapSat[\hs]{n}{W} \\
&\qquad\text{ iff }\\
&\exists R : \dom(W) \rightarrow \HeapSegments \ldotp & &\\
&\quad\begin{aligned}
  &\hs = \biguplus_{r \in \dom(W)} R(r) \\
  &\qquad\text{and}\\
  &\forall r \in \dom(W) \ldotp \forall n' < n \ldotp \npair[n']{R(r)} \in W(r).H(W(r).s)(\xi^{-1}(W))
\end{aligned} 
\end{align*}
\end{definition}

>>>>

%% make latex preview-mode work with natbib...
\usepackage[displaymath,floats,graphics,textmath,footnotes]{preview}

@@

\subsection{Variant of the ``awkward'' example}
Assembly variant of the ``awkward'' example from \citep[p.~11]{Dreyer:2010:IHS:1863543.1863566}. 
\begin{verbatim}
let h = fun adv =>
          let x = 1 in
          let g = fun adv =>
                    x := 0;
                    adv(g);
                    x := 1;
                    adv(g);
                    assert(x == 1) in
          g(g)
\end{verbatim}
In Dreyer's example, the issue arises as the context can provide the result of evaluating $\mathtt{e_1}$ (the equivalent here is \texttt{g})) to \texttt{f} (the equivalent here is \texttt{adv}). In our system, the context cannot capture this, so in the above program, \texttt{adv} is given explicit access to \texttt{g}. The lemma we would want to prove here is that the assertion does not fail.

@@

Erase all but a set of views:
\begin{align*}
  \lfloor W \rfloor_S \defeq \lambda r \ldotp 
  \begin{cases}
    W(r) & W(r).v \in S\\
    \bot & \text{otherwise}
  \end{cases}
\end{align*}

Heap satisfaction:
\begin{align*}
  &\heapSat[\hs]{n}{W} \\
  &\qquad\text{ iff }\\
  &\begin{aligned}[t]
    &\exists R : \dom(\erase{W}{\perma,\temp}) \rightarrow \HeapSegments \ldotp \\
    &\quad \hs = \uplus_{r\in\dom(\erase{W}{\perma,\temp})}R(r) \land \\
    &\quad \forall r \in \dom(\erase{W}{\perma,\temp}) \ldotp\\
    &\qquad \forall n'<n \ldotp \\
    &\qquad \quad \exists H,s \ldotp\\
    &\qquad \qquad W(r) = (\_,s,\_,H) \land \\
    &\qquad \qquad \npair[n']{R(r)} \in H(s)(\xi^{-1}(W))\\
  \end{aligned}
\end{align*}

@@

\begin{definition}[Heap satisfaction/erasure]
\begin{align*}
&\heapSat[\hs]{n}{W} \\
&\qquad\text{ iff }\\
&\exists R : \dom(W) \rightarrow \HeapSegments \ldotp & &\\
&\quad\begin{aligned}
  &\hs = \biguplus_{r \in \dom(W)} R(r) \\
  &\qquad\text{and}\\
  &\forall r \in \dom(W) \ldotp \forall n' < n \ldotp \npair[n']{R(r)} \in W(r).H(W(r).s)(\xi^{-1}(W))
\end{aligned} 
\end{align*}
o\end{definition}
